### 2024-11-14 conteudo/methods/methods.tex
fix some verbal times, i believe it is correct now

We apply two independent methods and perform triangulation on the results. The first method evaluates the proposed tool using an approach from the literature, comparing it against the BigCloneBench dataset \citep{bigclonebench}. The second method is an empirical analysis of a subset of functions within the AMD Display driver that our tool identified as duplicates. After completing these two methods, we will triangulate the findings to analyze the results comprehensively. We chose triangulation because relying solely on the literature-based method has limitations and may not be entirely reliable \citep{bigfail, litreview}.

@@

Ethnography is a recognized qualitative empirical method for understanding people, their cultures, and their work practices \citep{bookethno}. It allows researchers to gain insights into values, beliefs, and ideas from the perspective of community members \citep{ethnosoft}. In our research, refactoring code duplications without community interaction would prevent us from understanding whether Linux maintainers would accept our approach or identify their concerns. Thus, we used ethnography, positioning ourselves as Linux kernel contributors focused on removing identified code duplications.

@@

As with the empirical analysis, evaluating every code duplication in the Linux kernel is impractical. Thus, we limited the experiment to the AMD Display driver and used random sampling of duplicated functions inferred by our tool to initiate the mitigation approach in Section \ref{subsec:pipeline}. We chose a sample size of 30 duplicated functions, as studies indicate this size provides statistical significance \citep{sample1, sample2}.

For random selection, we restricted eligibility to function pairs with a similarity metric of 100\%. With this criterion, we randomly chose functions from eligible pairs uniformly.

>>>>

We applied two independent methods and perform triangulation on the results. 
The first method evaluates the proposed tool using an approach from the literature, 
comparing it against the BigCloneBench dataset \citep{bigclonebench}. 
The second method is an empirical analysis of a subset of functions within the 
AMD Display driver that our tool identified as duplicates. After completing these two 
methods, we triangulated the findings to analyze the results comprehensively. 
We chose triangulation because relying solely on the literature-based method has 
limitations and may not be entirely reliable \citep{bigfail, litreview}.

@@

Ethnography is a recognized qualitative empirical method for understanding people, 
their cultures, and their work practices \citep{bookethno}. It allows researchers 
to gain insights into values, beliefs, and ideas from the perspective of community 
members \citep{ethnosoft}. In our research, refactoring code duplications without 
community interaction would prevent us from understanding whether Linux maintainers 
would accept our approach or identify their concerns. Thus, we will use ethnography, 
positioning ourselves as Linux kernel contributors focused on removing identified 
code duplications.

@@

As with the empirical analysis, evaluating every code duplication in the Linux kernel is impractical. 
Thus, we will limit the experiment to the AMD Display driver and used random sampling of duplicated functions
inferred by our tool to initiate the mitigation approach in Section \ref{subsec:pipeline}. 
We will choose a sample size of 30 duplicated functions, as studies indicate this size provides 
statistical significance \citep{sample1, sample2}.

For random selection, we will restrict the eligibility to function pairs with a similarity metric of 100\%. 
With this criterion, we randomly chose functions from eligible pairs uniformly.
